Storing messages with multipartite neural cliques

### 2014-07-09 Articles/article.tex
Début description algo
...

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).

		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$}
		\Procedure{Sum of sum}{$v, w$}
		%\Statex
		\While{$s < I$}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

>>>>

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).
		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s = \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}
